Clinical prediction using similarity cohort--based models: A systematic scoping review

### 2025-03-14 docs/Localized-Modeling-BMCAI/localized-modeling-dai-revision.Rmd
fix reference formatting

## Challenges\hl{ with methods}

@@

\hl{As in the case of data and, recently, of ML models, having a standardized general framework facilitates the recombination of ideas and prevents duplicate effort as well as supporting more comprehensive and efficient work [@Ravi2022]. A SCBM implementation based on this framework would help investigators systematically compare predictions and other output obtained using different tools for cohort retrieval and predictive modeling, as well as tune the parameters governing these tools. It would also make like-kind comparisons of performance easier on different tasks using different data sets and expedite validation studies. This would address the core technical needs expressed in our sample (Section }\ref{identified-needs}\hl{) as well as the limitations of our own comparison of reported performances (Section }\ref{evaluations}\hl{).
We also believe that this framework could be used to make the diversity of possible approaches more comprehensible to users, enabling them to most appropriately tailor these decisions to their tasks.}

@@

## Rationales\hl{ for methods}

>>>>

## Challenges\hl{ faced}

@@

\hl{As in the case of data and, recently, of ML models, having a standardized general framework facilitates the recombination of ideas and prevents duplicate effort as well as supporting more comprehensive and efficient work }[@Ravi2022]\hl{. A SCBM implementation based on this framework would help investigators systematically compare predictions and other output obtained using different tools for cohort retrieval and predictive modeling, as well as tune the parameters governing these tools. It would also make like-kind comparisons of performance easier on different tasks using different data sets and expedite validation studies. This would address the core technical needs expressed in our sample (Section }\ref{identified-needs}\hl{) as well as the limitations of our own comparison of reported performances (Section }\ref{evaluations}\hl{).
We also believe that this framework could be used to make the diversity of possible approaches more comprehensible to users, enabling them to most appropriately tailor these decisions to their tasks.}

@@

## Rationales\hl{ for proposed methods}

### 2025-03-14 docs/Localized-Modeling-BMCAI/localized-modeling-dai-revision.tex
fix reference formatting

\subsection{\texorpdfstring{Challenges\hl{ with methods}}{Challenges}}\label{challenges}

@@

\hl{As in the case of data and, recently, of ML models, having a standardized general framework facilitates the recombination of ideas and prevents duplicate effort as well as supporting more comprehensive and efficient work [@Ravi2022]. A SCBM implementation based on this framework would help investigators systematically compare predictions and other output obtained using different tools for cohort retrieval and predictive modeling, as well as tune the parameters governing these tools. It would also make like-kind comparisons of performance easier on different tasks using different data sets and expedite validation studies. This would address the core technical needs expressed in our sample (Section }\ref{identified-needs}\hl{) as well as the limitations of our own comparison of reported performances (Section }\ref{evaluations}\hl{).
We also believe that this framework could be used to make the diversity of possible approaches more comprehensible to users, enabling them to most appropriately tailor these decisions to their tasks.}

@@

\subsection{\texorpdfstring{Rationales\hl{ for methods}}{Rationales}}\label{rationales}

>>>>

\subsection{\texorpdfstring{Challenges\hl{ faced}}{Challenges}}\label{challenges}

@@

\hl{As in the case of data and, recently, of ML models, having a standardized general framework facilitates the recombination of ideas and prevents duplicate effort as well as supporting more comprehensive and efficient work }\citep{Ravi2022}\hl{. A SCBM implementation based on this framework would help investigators systematically compare predictions and other output obtained using different tools for cohort retrieval and predictive modeling, as well as tune the parameters governing these tools. It would also make like-kind comparisons of performance easier on different tasks using different data sets and expedite validation studies. This would address the core technical needs expressed in our sample (Section }\ref{identified-needs}\hl{) as well as the limitations of our own comparison of reported performances (Section }\ref{evaluations}\hl{).
We also believe that this framework could be used to make the diversity of possible approaches more comprehensible to users, enabling them to most appropriately tailor these decisions to their tasks.}

@@

\subsection{\texorpdfstring{Rationales\hl{ for proposed methods}}{Rationales}}\label{rationales}
